LAGOS lake depth

### 2020-11-10 figures/01_geometry.Rmd
prototype slope x shape x depth x area comparison figure #21

>>>>

```{r slope_by_area_depth, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5.5, fig.height=4.2}

nearshore     <- read.csv("../data/00_geometry/nearshore.csv",
                      stringsAsFactors = FALSE) %>%
                  dplyr::select(-inlake_slope)
dt_raw        <- read.csv("../data/lagosus_depth_predictors.csv", 
                      stringsAsFactors = FALSE) %>%
                  left_join(nearshore, b = c("lagoslakeid" = "llid")) %>% 
                  dplyr::filter(shape_class %in% c("concave", "convex")) %>% 
                  dplyr::filter(inlake_slope < 0.6)

breaks_dt <- classInt::classIntervals(dt_raw$lake_waterarea_ha, n = 4)$brks
dt        <- dt_raw %>%
  dplyr::mutate(x_bins = cut(dt_raw$lake_waterarea_ha,
      breaks = breaks_dt)) %>%
  dplyr::filter(!is.na(x_bins))
dt <- dt %>%
  dplyr::mutate(x_bins = forcats::fct_recode(x_bins, 
        !!!setNames(levels(dt$x_bins), 
                    paste0("< ", as.character(round(breaks_dt[-1], 1))))
      )
    )

gg_area <- ggplot(data = dt) +
   geom_point(aes(x = slope_mean, y = inlake_slope, color = x_bins)) +
   geom_smooth(aes(slope_mean, inlake_slope, color = x_bins),
               method = "lm", se = FALSE) + 
  facet_wrap(~shape_class) +
    ggtitle("Area (ha)")

breaks_dt <- classInt::classIntervals(dt_raw$lake_maxdepth_m, n = 4)$brks
dt        <- dt_raw %>%
  dplyr::mutate(x_bins = cut(dt_raw$lake_maxdepth_m,
      breaks = breaks_dt)) %>%
  dplyr::filter(!is.na(x_bins))
dt <- dt %>%
  dplyr::mutate(x_bins = forcats::fct_recode(x_bins, 
        !!!setNames(levels(dt$x_bins), 
                    paste0("< ", as.character(round(breaks_dt[-1], 1))))
      )
    )

gg_depth <- ggplot(data = dt) +
   geom_point(aes(x = slope_mean, y = inlake_slope, color = x_bins)) +
   geom_smooth(aes(slope_mean, inlake_slope, color = x_bins),
               method = "lm", se = FALSE) +
    facet_wrap(~shape_class) +
    ggtitle("Max Depth (m)")

theme_opts <- cowplot::theme_cowplot() +
  theme(legend.position = "bottom", 
        legend.title = element_blank(), 
        panel.spacing = unit(1, "lines")) 
cowplot::plot_grid(
  gg_area + theme_opts +
    guides(color = guide_legend(nrow = 2, byrow = TRUE)),
  gg_depth + theme_opts + 
    theme(axis.title.y = element_blank(), 
          axis.text.y = element_blank(), 
          axis.line.y = element_blank(),
          axis.ticks.y = element_blank()) +
    guides(color = guide_legend(nrow = 2, byrow = TRUE)),
  rel_widths = c(1, 0.87))
